% examples/03-paper-with-citations/src/paper.tex

\DocumentMetadata{
  pdfversion = 2.0,
  pdfstandard = ua-2,
  pdfstandard = a-4f,
  lang = en-GB,
}

\documentclass[final,tagged]{pub-paper}

\title{A Short Note on Accessible Publishing}
\author{Example Author}

\begin{document}

\maketitle

\begin{abstract}
We outline three forces shaping tagged-PDF tooling in 2026: the EU
EAA's first audit year~\cite{eaa-2025}, the maturation of
\texttt{tagpdf} v1~\cite{tagpdf-v1}, and the convergence of agentic
publishing pipelines on the Model Context Protocol~\cite{mcp-2026}.
\end{abstract}

\section{Background}

The accessibility, archival, and authenticity floors of digital
publishing rose dramatically over 2024--2026. Inclusio sits at
their intersection.

\section{Forces}

\paragraph{EAA.} The European Accessibility Act started enforcement
on 28 June 2025~\cite{eaa-2025}; 2026 is the first full audit year.

\paragraph{tagpdf.} The LaTeX kernel's per-class tagging support
shipped general-availability in \texttt{tagpdf} v1.0b in April
2026~\cite{tagpdf-v1}.

\paragraph{MCP.} The Model Context Protocol release candidate
(July 2026) introduces \emph{Tasks} for long-running pipelines, a
natural fit for typeset $\rightarrow$ audit $\rightarrow$ sign
chains~\cite{mcp-2026}.

\begin{thebibliography}{9}
  \bibitem{eaa-2025} European Commission,
  \emph{European Accessibility Act}, 2025.
  \bibitem{tagpdf-v1} U. Fischer, \emph{The tagpdf package, version
  1.0b}, 24 April 2026.
  \bibitem{mcp-2026} Anthropic et al.,
  \emph{Model Context Protocol — 2026-07-28 RC}, 2026.
\end{thebibliography}

\end{document}
